---
title: "Online Exercise - R Notebook"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

## Online Exercise - Topic 3: Wordcloud to analyze tweets ##
### Introduction to R FS 20 UZH ###
### Tobias Boner 17-707-878 ###

In this R notebook we will provide a step by step guide to create a wordcloud. Therefore, we use the wordcloud() function to analyze tweets (corona_tweets.csv)

This work will adress the following points:

1. What is the reason for plotting a word cloud representing Tweets?
2. What are the steps in plotting Tweets?
    + List and explain the specific steps to prepare the input data.
    + Explain your reasoning for all steps, e.g. subsetting the data, creating new variables, manipulating data structures.
    + Which variables do you include and why?
    + Make sure the graph makes sense and is visually appealing (i.e. remove irrelevant words, coloring of important words).
3. Show and interpret the word cloud you created.
4. Summary




#### **Step 1:** ####
##### Load and (install --> only needed once) all nececessary packages #####

```{r}

### load packages ###
library(data.table)
library(lubridate)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)

# shows you all installed packages
installed.packages()

```

#### **Step 2:** ####
#####load the data that entails the tweets ######
```{r}
data <- fread("corona_tweets.csv")
```

#### **Step 3:** ####
#### Inspect the data and its properties ####
```{r}
# inspect properties of data
str(data)

# print the data
data

# show column names of data
colnames(data)

# get first column of data
data[, "V1"]
data[, 1]

# get more columns of data
data[, "text"]
data[,4]
data[,16]

# get rows of data
data[1,]
data[1:10,]



```

